Towards a reproducible framework for undergraduate data science research

### 2019-11-30 Rmd/methods.Rmd
fixed headers

## Methods

@@

### Broaden statistical computing to include emerging areas

@@

### deepen computational reasoning skills

@@

### combine computational topics with data analysis in the practice of statistics

@@

### data analysis and practice of statistics

>>>>

# Methods

@@

## Broaden statistical computing to include emerging areas

@@

## Deepen computational reasoning skills

@@

## Combine computational topics with data analysis in the practice of statistics

@@

## Implementation of the framework
